eyeIntegration Viewing Stats

### 2019-10-07 src/viewing_stats.Rmd
updated plot, now collects info by date

```{r}
library(tidyverse)
library(rworldmap)
library(ipstack)
ipaddresses <- read_delim('~/Desktop/stats/eyeIntegration.stats', col_names = F, delim = '\\s+') %>% 
  separate(col = X1, into = c('IP Address', 'Page Views'), sep='\\s+') %>% 
  mutate(`Page Views` = as.numeric(`Page Views`)) %>%  
  filter(`Page Views` > 11)
```

Total page view from May 2017 to November 2017
```{r}
sum(ipaddresses$`Page Views`)
```

Get latitude and longitude for all unique IPs (takes a few minutes to query)
```{r}
unique_IP <- ipaddresses$`IP Address` %>% unique()
ip_info <- list()
for (i in unique_IP){
  ip_info[[i]] <- ip_lookup(i, ipstack_api_key = '7d06f26c4f0f61bd9edd20df0219f874', hostname = T)
}

@@

Process and clean up
```{r}
ips <- ''
latitudes <- ''
longitudes <- ''
cities <- ''
countries <- ''
for (i in unique_IP){
  if (!is.null(ip_info[[i]]$country_name)){
  ips <- c(ips, ip_info[[i]]$ip)
  latitudes <- c(latitudes, ip_info[[i]]$latitude)
  longitudes <- c(longitudes, ip_info[[i]]$longitude)
  cities <- c(cities, ip_info[[i]]$city)
  countries <- c(countries, ip_info[[i]]$country_name)
  }
}

@@

Regular Map
```{r, fig.width = 6, fig.height=2}
ggplot(data = geo_locate, aes(x = longitudes, y = latitudes, colour = countries)) + 
  geom_map(data=world, map=world,
           aes(x=long, y=lat, map_id=region),
           color="#090D2A", fill="lightgray", size=0.05, alpha=1/4) + 
  geom_point() + 
  theme_void() +
  scale_color_viridis_d()

>>>>

```{r}
library(tidyverse)
library(rworldmap)
library(ipstack)
ipaddresses <- read_delim('~/Desktop/email_eyeintegration_//eyeIntegration.stats', col_names = F, delim = '\\s+') %>% 
  separate(col = X1, into = c('IP Address', 'Page Views'), sep='\\s+') %>% 
  mutate(`Page Views` = as.numeric(`Page Views`)) %>%  
  filter(`Page Views` > 11)
```

```{r}
files <- list.files('~/Desktop/email_eyeintegration_/', pattern = '*eml', full.names = TRUE)
eml <- files %>% map(read_lines) 
dates <- eml %>% 
  map(grep, pattern = 'Date:', value =TRUE) %>% 
  map(gsub, pattern = 'Date: \\w+, | \\d+:.*', replacement = '') %>% 
  map(as.Date, format = "%d %b %Y") %>% 
  map(as.character) %>% 
  unlist() %>% 
  as.Date()
ip <- eml %>% 
  map(grep, pattern = '^[[:digit:]]', value = TRUE) %>% 
  map(str_split, pattern = '\\s+') %>% 
  set_names(dates)

empty_list <- ip %>% map(length) %>% unlist()
empty_list <- empty_list != 0
ip <- ip[empty_list]

ip <- ip %>% map(enframe) %>% map(unnest_wider, value) %>% bind_rows(.id = 'Date')
colnames(ip) <- c('Date', 'Name', 'IP', 'Pages')
ip$Pages <- as.numeric(ip$Pages)
```

Total page views from May 2017 to Today
```{r}
sum(ip$Pages)
```

Get latitude and longitude for all unique IPs (takes a few minutes to query)
```{r}
unique_IP <- ip$IP %>% unique()
ip_info <- list()
for (i in unique_IP){
  ip_info[[i]] <- ip_lookup(i, ipstack_api_key = '7d06f26c4f0f61bd9edd20df0219f874', hostname = T)
}

@@

Process and clean up
```{r}
ips <- ''
latitudes <- ''
longitudes <- ''
cities <- ''
countries <- ''
hostname <- ''
for (i in unique_IP){
  if (!is.null(ip_info[[i]]$country_name)){
  ips <- c(ips, ip_info[[i]]$ip)
  hostname <- c(hostname, ip_info[[i]]$hostname)
  latitudes <- c(latitudes, ip_info[[i]]$latitude)
  longitudes <- c(longitudes, ip_info[[i]]$longitude)
  cities <- c(cities, ip_info[[i]]$city)
  countries <- c(countries, ip_info[[i]]$country_name)
  }
}

@@

Regular Map
```{r, fig.width = 6, fig.height=2}
world <- map_data("world")
world <- world[world$region != "Antarctica",]
ggplot(data = geo_locate, aes(x = longitudes, y = latitudes, colour = countries)) + 
  geom_map(data=world, map=world,
           aes(x=long, y=lat, map_id=region),
           color="#090D2A", fill="lightgray", size=0.05, alpha=1/4) + 
  geom_point() + 
  theme_void() +
  scale_color_viridis_d()
```

Page View over Time
```{r}
ip$Date <- as.Date(ip$Date)
ip %>% 
  filter(Pages > 11) %>% 
  arrange(Date) %>% 
  ggplot(aes(x=Date, y = cumsum(Pages)/10)) + 
  geom_line() + cowplot::theme_cowplot()  + ylab("Cumulative Queries")
```
